\subsection{Purpose of this document}

Since the war "somewhere in the Middle East", the amount of fuel has drastically decreased. As a result, the government has decided to implement a nation wide fuel rationing system to ensure that all citizens have equal access to the resource. This document is meant to describe the involved parties, requirements and design decisions of a such a system. 

\subsection{Target audience}

This document is meant to be read by the government officials who are charged with seeing this project to completion. The sections which describe the requirements and the protocol specifications are meant for the hardware manufacturers. The petrol companies and gas station managers may also find this the information of this document informative to understand the underlying details of the system. Lastly, the document should be made public such that card owners can access it for the purpose of understanding how the system deals with lost cards.

\subsection{Strucure}

The document is structured into seven sections as follows:
\begin{enumerate}
  \item The introduction.
  \item Use cases for the petrol rationing system.
  \item A listing of all the assets which make up the system.
  \item A listing of all parties involved in this project and their responsabilities.
  \item The model of the attacker which we considered when designing the protocol.
  \item The security requirements which the protocol implements to mitigate any possible attacks.
  \item The full description of the protocol.
\end{enumerate}