\subsubsection{Lost Cards}
Cards may be misplaced or stolen. The first layer of defence against abuse by an attacker is the card PIN. This 4-digit PIN would have been randomly generated during card personalisation and not known to the attacker. PIN authentication is also carried out only after an authenticated and encrypted channel is created between the card and terminal - it cannot be eavesdropped by a MITM attack or a fake terminal. 

Additionally, cards only allow three consecutive wrong PIN entries before the card is locked and all functionality prohibited. Locked cards can be re-activated by the legitimate card owner at government centres where human staff can physically authenticate the card owner e.g. against identity cards.

The next layer of defence is for the Government CA to revoke cards which are reported to be misplaced or stolen. This is updated in the back-end database to which charging terminals are connected. When a revoked card is presented to a charging terminal, the charging terminal will disable the card by toggling a 'REVOKE-FLAG' within the card.

A third layer of defence for lost cards is to limit the amount of petrol withdrawals it can make in between each visit to the charging terminal. As such, cards can only make five withdrawals (which also tallies with the log space) and the total of these withdrawals cannot exceed 250 litres (which is 125\% the monthly charging allowance of 200 litres).

Another potential solution is for petrol terminals to check the revocation status of the cards. Manually updating the certificate revocation list (CRL) within the pumps is not an efficient solution. More ideally, petrol terminals are online and are able to query the Government CA to check the revocation status by OCSP. However, we will not implement this in the project as this has more to do with the backend.

\subsubsection{Compromised Petrol Terminals}
The possibility of private keys within petrol terminals being compromised is very rare. Nevertheless, the impact can be significant as fraudulent deductions by compromised terminals can create public mistrust in the rationing system. This threat is mitigated by loading CRLs (consisting of compromised petrol terminals) onto ration cards each time they visit a charging terminal. Ration cards will check the petrol terminal identity against the CRL before continuing the transaction.